DNSKEY Management

### 2012-12-02 paper/paper.tex
Write more about DNSSEC penetration

\usepackage{graphicx}

@@

In figure~\ref{fig:dnssec-growth} you can see the development of
deployed, production DNSSEC zones (for the heuristics applied to
determine a production zone, see \cite{secspider, Osterweil09}).

@@

Contrary to the state at writing of \cite{Osterweil09}, the DNS
root-zone is signed since July 15, 2010 \cite{root-dnssec} and hence
serves as the global trust anchor.

>>>>

\usepackage{graphicx}
\usepackage{url}

@@

In figure~\ref{fig:dnssec-growth} you can see the development of
deployed, production DNSSEC zones (for the heuristics applied to
determine a production zone, see \cite{secspider, Osterweil09}). We
can see that DNSSEC is gradually being deployed.

Contrary to the state at writing of \cite{Osterweil09}, the DNS
root-zone is signed since July 15, 2010 \cite{root-dnssec} and hence
serves as the global trust anchor. However, as of this writing,
data\footnote{\url{http://secspider.cs.ucla.edu/islands.html}}
gathered by \cite{secspider} suggests that more than half of the
deployed DNSSEC zones which are verifyable (i.e. are likely not to
have a spoofed key, see \cite{Osterweil09} for details), do not yet
have a fully linked certificate chain up to the root zone.

@@
